Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-06 sections/04-application.tex
Update on Overleaf.

The data contains eight nowcasts from scientific and public institutions, nowcast communities, and a newspaper, using different input variables, calendar data, and length of training data.
The model structures are diverse, including Bayesian models, generalized additive models, and parametric bootstrapping.
Table~\ref{tab:app-covid-models} in the appendix lists the different abbreviations together with the respective names in the COVID19-Nowcasting-Hub.
For information on the model design, we refer to~\textcite{Wolffram2023}.
Using the nowcasts, two ensemble methods are constructed using the ensembles' mean or median.
We denote them by ENS-MEAN and ENS-MED.
\textcite{Wolffram2023} describes the design of the nowcast tasks and the data submission guidelines for the teams that was stated in a preregistered study. 
In line with the initial study design, we consider the period from November 22, 2021, to April 29, 2022, as the evaluation period.
In contrast to~\textcite{Wolffram2023}, we use the newest data available on the true values, not the data from August 8, 2022.
\unsure{Nochmal längere Evaluation?}
We do not expand on the models' performance on specific regions or age groups in Germany and the probabilistic nowcast assessment.
Figure~\ref{fig:app-covid-true-nowcast} displays the true and nowcast data for the evaluation period.
The time comprises the fourth wave's end in December 2021 and nearly the entire fifth wave of the pandemic in Germany, lasting until May 28, 2022~\parencite{Tolksdorf2022}.
Table~\ref{tab:app-covid-rmse} summarizes the point evaluation measures for the issued mean of the different models.
The models issue same-day nowcasts for nearly all 159 days of the evaluation period~\parencite[see][Tables A2, A3, and A4]{Wolffram2023}.
The best-performing models in terms of RMSE and MAE are the ILM and RKI models.
The ensemble methods perform worse than the best models regarding the mean location.
The performance of the models is diverse, with more than twice as high RMSE values for the worst models compared to the best models.
Note that the high values for the EPI model could be driven by an exceptionally far-off value at the end of the evaluation period.

>>>>

The data contains eight nowcasts from scientific and public institutions, nowcast communities, and a newspaper, using different input variables, calendar data, and length of training data.
The model structures are diverse, including Bayesian models, generalized additive models, and parametric bootstrapping.
Table~\ref{tab:app-covid-models} in the appendix lists the different abbreviations together with the respective names in the COVID19-Nowcasting-Hub.
For information on the model design, we refer to~\textcite{Wolffram2023}.
Using the nowcasts, two ensemble methods are constructed using the ensembles' mean or median.
We denote them by ENS-MEAN and ENS-MED.
\textcite{Wolffram2023} describes the design of the nowcast tasks and the data submission guidelines for the teams that were stated in a preregistered study. 
In line with the initial study design, we consider the period from November 22, 2021, to April 29, 2022, as the evaluation period.
In contrast to~\textcite{Wolffram2023}, we use the newest data available on the true values, not the data from August 8, 2022.

We do not expand on the models' performance on specific regions or age groups in Germany and the probabilistic nowcast assessment.
Figure~\ref{fig:app-covid-true-nowcast} displays the true and nowcast data for the evaluation period.
The time comprises the fourth wave's end in December 2021 and nearly the entire fifth wave of the pandemic in Germany, lasting until May 28, 2022~\parencite{Tolksdorf2022}.
Table~\ref{tab:app-covid-rmse} summarizes the point evaluation measures for the issued mean of the different models.
The models issue same-day nowcasts for nearly all 159 days of the evaluation period~\parencite[see][Tables A2, A3, and A4]{Wolffram2023}.
The best-performing models in terms of RMSE and MAE are the ILM and RKI models.
The ensemble methods perform worse than the best models regarding the mean location.
The performance of the models is diverse, with more than twice as high RMSE values for the worst models compared to the best models.
Note that the high values for the EPI model could be driven by an exceptionally far-off value at the end of the evaluation period.
